---
title: "End of course 212"
format:
  html:
    theme: default
    toc: true
    number-sections: true
---

The End!!!

```{r}
library(tidyverse)
```

# Some logical operators

-   == (does this match),

-   single = means this equals,

-   != (do these not match? )

-   \<,\>, \>=, \<=

-   &, \|

-   boolean = true or false

```{r}
#this is a question, does 4 match 5
 4 == 5
```

```{r}
#does not 4 match 4
4 == 4
```

```{r}
#does 4 not match 5

4 != 5
```

```{r}
#does 4 match "4"
4 == "4"

#with assignment varabibles 
cat <- 10
dog <- 7

```

```{r}
cat > dog 

```

```{r}
#is dog greater than cat or cat less than 20, vertical line is "or" one of these staments is true
dog > cat | cat < 20
```

```{r}
#is dog less than cat and is cat equal to 10
dog < cat & cat == 10
```

```{r}
dog > (0.5 *cat)
```

```{r}
dog < cat & cat > 2 & 4 >= dog
```

```{r}
mtcars
```

```{r}
ggplot(data = mtcars, aes(x = wt, y = mpg)) +
  geom_point(color = "red", aes(size = mpg, color = wt)) +
  labs(x = "Car weight (1000 pounds)",
       y = "Gas mileage (mpg)", 
       title = "Car weight efficiency relationship")
```
